Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-09-30 ms/ms.Rmd
ms: Ørskog sample size

Subsubsection text here.

>>>>

At Ørskogfjellet we also measured peat depth in a sample of \unit{10\,m} raster cells, selected from the part of the study area classified in the AR5 dataset as mire.
Before selecting locations, we determined a minimal sample size that would adequately capture the terrain and radiometric properties of the entire mire area.
Specifically, we aimed to identify the size at which adding locations produced diminishing decreases in divergence between sample and population distributions --- i.e. the elbow point in a curve of similarity between sample and population [@maloneMethodsImproveUtility2019].
This approach has been found to identify sample sizes that correspond with diminishing returns in predictive model performance on external evaluation data [@sauretteDivergenceMetricsDetermining2023].
We defined a sequence of increasing sample sizes (50--500) and for ten replicate samples at each size [drawn by conditioned latin hypercube sampling, @minasnyConditionedLatinHypercube2006; @roudierClhsPackageConditioned2011], we calculated the mean Kullback-Leibler divergence between sample and population distributions [@maloneMethodsImproveUtility2019; @sauretteDivergenceMetricsDetermining2023].
The variables in the divergence calculation were terrain slope and four radiometrics: potassium, thorium, uranium, and total count.
Next, we fitted a asymptotic regression of mean divergence on sample size, and identified the sample size at which the curve reached 95 % of the fitted asymptote.
Through this procedure we found that we could adequately capture the population distribution with a sample of 160 locations.

### 2024-09-30 ms/ms.tex
ms: Ørskog sample size

Subsubsection text here.

>>>>

At Ørskogfjellet we also measured peat depth in a sample of \unit{10\,m} raster cells, selected from the part of the study area classified in the AR5 dataset as mire.
Before selecting locations, we determined a minimal sample size that would adequately capture the terrain and radiometric properties of the entire mire area.
Specifically, we aimed to identify the size at which adding locations produced diminishing decreases in divergence between sample and population distributions --- i.e.~the elbow point in a curve of similarity between sample and population \citep{maloneMethodsImproveUtility2019}.
This approach has been found to identify sample sizes that correspond with diminishing returns in predictive model performance on external evaluation data \citep{sauretteDivergenceMetricsDetermining2023}.
We defined a sequence of increasing sample sizes (50--500) and for ten replicate samples at each size \citep[drawn by conditioned latin hypercube sampling,][]{minasnyConditionedLatinHypercube2006, roudierClhsPackageConditioned2011}, we calculated the mean Kullback-Leibler divergence between sample and population distributions \citep{maloneMethodsImproveUtility2019, sauretteDivergenceMetricsDetermining2023}.
The variables in the divergence calculation were terrain slope and four radiometrics: potassium, thorium, uranium, and total count.
Next, we fitted a asymptotic regression of mean divergence on sample size, and identified the sample size at which the curve reached 95 \% of the fitted asymptote.
Through this procedure we found that we could adequately capture the population distribution with a sample of 160 locations.
